### 2016-05-16 text/ms.Rmd
Copy editing

<!-- \tableofcontents -->

@@

Status and trend are two of the most fundamental values to quantify in the
management of ecological populations [e.g. @iucn2015]. However, managers are
often faced with reconciling multiple uncertain and potentially conflicting
estimates of status and trend [e.g. @brodziak2010; @branch2011; @deroba2015].
For example, one model may suggest a population is at risk and declining in
abundance while others may suggest it is not at risk and stable.

@@

In fisheries science, the commonly used operational models for determining
status and trend of exploited fish populations are stock assessments, i.e.,
population models coupled to an observation model, that incorporate all
appropriate data (e.g. catches, size and age distributions, surveys, and
tagging information) to quantify values such as the biomass of a stock that
can produce maximum sustainable yield ($B_\mathrm{MSY}$) [@hilborn1992].
However, the broad range of data required to conduct these stock assessments
are not available for the majority of fish populations, including those of
conservation concern and of economic interest to fisheries [@fao2014].

Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$
based on the limited data available for the majority of fish stocks: (1) a time
series of the total biomass of catch and (2) a basic understanding of
population productivity [e.g. @vasconcellos2005; @martell2013]. Recently,
@rosenberg2014 investigated the performance of four data-limited models through
a large-scale simulation experiment. Three of these models were based on
Schaefer (logistic) biomass dynamics and one was an empirical model fitted to
more data-rich stock-assessment output. The four models frequently disagreed
about population status (e.g. Fig. \ref{motivate}), no one model had strong
performance across all fish stocks, and some models performed better than
others depending on circumstances.

@@

<!--
Structure of methods: summary of methods
 1. indiviudla models
 2. ensemble models
 3. additional covariates
 4. data used to test and cross validation,
 5. testing model perforance. -->

@@

We first developed and tested ensemble methods on a fully factorial simulated
dataset of fisheries [@rosenberg2014] with known status. These simulated data
included the following scenarios: three fish life histories: small pelagic,
demersal, and large pelagic; three levels of initial biomass depletion
compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying
capacity; and four exploitation settings: (1) a constant exploitation rate,
(2) an exploitation rate coupled with biomass to mimic an open-access
single-species fishery, (3) a scenario where exploitation rate increased
continuously, and (4) a 'roller-coaster' scenario where the exploitation
rate increased and then decreased. Process noise (recruitment variability;
i.e. unexplained variability in population dynamics) was introduced to the
models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$,
and was either uncorrelated through time or had first-order autoregressive
correlation of $0.6$. The simulation also included a scenario with $N(0,
0.2^2)$ measurement error around log(catch) and one scenario without
measurement error. @rosenberg2014 ran ten iterations for each combination
of factors adding stochastic draws of recruitment and catch-recording
variability each time to generate a total of 5760 stocks. The simulation
models were built in the `FLR` packages [@kell2007,
<http://flr-project.org>] for the statistical software R. Code to
generate the simulations is available at
<https://github.com/iagomosqueira/stockStatusFAO>.

@@

The individual models we seek to combine with superensembles provide time
series of stock status ($B/B_\mathrm{MSY}$). Therefore, we can use
superensembles to estimate any property of these time series. Here, we focus
on two properties: the mean and slope of $B/B_\mathrm{MSY}$ in the last five
years. Together, these quantities address the recent state and trend of stock
status, which are both of management and conservation interest [e.g.
@mace2008] TODO add fishery REF. To avoid undue influence of the end points of
the time series on the calculated slope, we measured the slope as the
Theil-Sen estimator of median slope [@theil1950].

@@

We compared an ensemble average and three superensembles of varying
complexity: a linear model with two-way interactions, a random forest, and a
boosted regression tree. We describe these models as estimating
$\hat{\theta}$, which represents either the ensemble estimated $\log
B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$. The individual model
estimates of $\log B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$ are
represented as $\hat{b}$ for models $i$ $1$ through $n$. The subscript $j$
indexes the simulated fisheries from $1$ through $m$. The ensemble average was
calculated as:

\begin{equation}
\hat{\theta_j} = \frac{1}{n} \sum_{i=1}^n \hat{b}_{i,j} , \quad
\mathrm{for}\ j  =  1,...,m.
\end{equation}

@@

\begin{equation}
\hat{\theta_j} = \beta_0 + \beta_1 \hat{b}_{j,0} + ... +
\beta_{1,2} \hat{b}_{j,1} \hat{b}_{j,2} + ... +
\epsilon_j,
\quad
\epsilon \sim \mathrm{Normal}(0, \sigma^2),
\quad \mathrm{for}\ j  =  1,...,m.
\end{equation}

Our two machine learning superensemble models, a random forest and a
generalized boosted model (GBM), were based on regression trees. Regression
trees sequentially determine what value of a predictor best splits the
response data into two 'branches' based on a loss function [@breiman1984]. In
random forests, a series of regression trees are built on a random subset of
the data and random subset of the covariates of the model [@breiman2001]. In
GBMs, each subsequent model is fit to the residuals from the previous model;
data points that are fit poorly in a given model are given more weight in the
next model [@elith2008]. Random forests and GBMs can provide strong predictive
performance and fit highly non-linear relationships [@elith2008; @hastie2009].
We fit random forest models with the `randomForest` package [@liaw2002] for R
with the default argument values. We fit boosted regression tree models with
the `gbm` package [@ridgeway2015] for R. We fit GBMs with 2000 trees, an
interaction depth of $6$, a learning rate (shrinkage parameter) of $0.01$, and
all other arguments at their default values.

@@

<!--TODO Kristin and Mark: It might be a good idea to add a figure that
illustrates the spectrum of ensemble/superensembles that are applied here and
what is included (e.g., non-linear relationships, etc.). This will help the
reader understand the progression in complexity of the ensemble approaches
I think. Jess: probably add this below the section explaining superensembles-->
<!-- TODO deal with removed spectral -->

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g. @walther2005]. Here, we
measure proportional error, defined as $(\hat{\theta} - \theta)/\abs{\theta}$,
where $\hat{\theta}$ and $\theta$ represent estimated and 'true' (or
stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median
proportional error to measure bias, median absolute proportional error to
measure accuracy, and Spearman's rank-order correlation between predicted and
'true' values to measure the ability to correctly rank populations. When
testing with the RAM Legacy Stock Assessment database, we treated the
estimates from these data-rich stock assessments as known without error. Thus,
any error in the stock-assessment estimates of the mean or slope of
$B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for
each of the four data-limited models and the ensembles. Code to reproduce our
analysis is available at <https://github.com/datalimited/ensembles> (*Private while in
review*).

@@

The superensemble models were able to improve the predictive performance by
harnessing the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high
clusters of predictions (Fig. \ref{partial-sim}). Superensembles also exploited
the covariance between individual model predictions. For instance, both the
linear model and GBM ensemble suggest that if mPRM and SSCOM predict high
status, the true status also tends to be high (Figs \ref{lm-coefs},
\ref{partial-2d-sim}l). The addition of spectral density covariates helped the
superensemble models correctly predict higher status values (Fig.
\ref{hexagon-sim-covariates}g, h). The performance of the ensembles was only
marginally improved by including these covariates (Fig.
\ref{performance-with-covariates} vs. Fig. \ref{performance}).

@@

Ensemble methods provide a useful approach to situations where environmental
resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status. Compared to individual models of
fish population status, ensemble methods were consistently the best or among
the best across three performance dimensions (accuracy, bias, and rank-order
correlation), two response variables (status and trend), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a simple
average to machine learning superensembles). Our results suggest choosing a
superensemble model that allows for non-parametric relationships, such as
machine learning methods. These methods provide added insight into individual
model behavior and generally performed the best; however, even a simple average
of predictions across multiple models may provide a more useful measure of the
desired parameter than a single model in many cases.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make uncorrelated
errors [@ali1996; @dietterich2000; @tebaldi2007]. Such individual models would
be expected to perform well in different conditions and an ensemble model can
exploit the best predictive performance of each superensembles. Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to overfitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we trained our superensembles on
the simulation dataset and tested them on a separate 'real' dataset (i.e. the
RAM Legacy Stock Assessment database, Fig. \ref{performance}b). Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically
biased impression of predictive performance if the training dataset
fundamentally differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criterion (AIC) is
a common analytical approach in fisheries and ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890].
A fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. Thus, ensembles
provide a general purpose tool: they do not require information theoretics
and they can combine different types of models (e.g. parametric and
non-parametric models or frequentist and Bayesian predictions). Furthermore,
superensembles extend these benefits by allowing model predictions to be
combined via non-linear functions that are tuned to known data.

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$ (Fig.
\ref{partial-sim}), but contributed strongly to estimates of trend (Fig.
\ref{partial-sim-slope}). Formally, fitting superensemble models to specific
quantities of interest provides an additional calibration step [@rykiel1996].
Individual models are typically calibrated (i.e. parameters are estimated) based
on a single response variable; however, this model might then provide a biased
or inaccurate estimate of other quantities of interest. Ensemble methods provide
a final calibration step to a quantity of interest. This ensemble calibration
could further include a loss function tailored to the goals of the model, say
placing greater weight on accuracy at low status levels than higher values.
Conversely, because superensembles are tailored to a specific response and loss
function, superensembles force a modeller to choose an operational purpose for
their model up front [*sensu* @dickey-collas2014].

As @box1987 noted, all models are wrong, but some may still be useful. The
ensemble methods we investigated attempt to piece together the useful parts of
candidate models to build a model with improved performance. Instead of viewing
the superensemble as a black box, we think considerable mechanistic
understanding can be gained by studying its structure. For example, when SSCOM
estimates very low status this is likely the case, conversely when COMSIR
estimates low status, the true status is more likely to be high (Fig.
\ref{partial-sim}). These models have two main differences: (1) the form of
effort dynamics and (2) the allowance for both measurement and process error in
SSCOM, whereas the implemented COMSIR admits measurement error only. Were the
methods to differ only in effort dynamics, the results point towards a more
suitable representation of effort dynamics at low biomasses in SSCOM. We think
that such investigation of the parameters of a superensemble may lead to
improvement in the mechanisms assumed in the individual models.

Combining predictions from multiple models via superensemble methods is also
broadly useful in other subfields of ecology and fisheries science. Predictions
about extinction risk are widely used at the national (e.g. the US Endangered
Species Act and the Canadian Species at Risk Act) and international [e.g. the
IUCN Red List, @iucn2015] levels. These risk assessments generally involve
fitting regression models to outcomes for individual species along with
predictors of extinction risk [e.g. @anderson2011a; @pinsky2011], or population
dynamics models to data for individual species [e.g. @dfo2010]. Both types of
models are prone to error caused by model-misspecification and therefore results
are sensitive to decisions about model structure [@brooks2015]. Although there
are options to account for potential model-misspecification in determination of
species risk [e.g. coefficient averaging, @burnham2002; generalized modeling,
@yeakel2011; or semi-parametric methods, @thorson2014], ensemble methods are
a relatively simple way to combine predictions in a transparent manner. Beyond
estimates of status and trend, ensemble methods could be used, for example, to
increase the robustness of spatial predictions when designing networks of
protected areas [@rassweiler2014] or to forecast potential spatial shifts in
species distribution given climate impacts [@harsch2014].

@@

We thank members of Phase I of the working group 'Developing new approaches to
global stock status assessment and fishery production potential of the seas'
who contributed to developing the data-limited methods and simulations used in
our analysis. We thank E. Jardim, F. Scott, and J.A. Hutchings for helpful
comments during the development of this project, and R.D. Methot for comments
on an earlier version of the manuscript. We thank the Gordon and Betty Moore
Foundation for funding the working group 'Applying data-limited stock status
models and developing management guidance for unassessed fish stocks'.

>>>>

\tableofcontents

@@

Status and trend are two of the most fundamental values to quantify in the
management of ecological populations [e.g. @hutchings2010; @iucn2015]. However,
managers are often faced with reconciling multiple uncertain and potentially
conflicting estimates of status and trend [e.g. @brodziak2010; @branch2011;
@deroba2015]. For example, one model may suggest a population is at risk and
declining in abundance while others may suggest it is not at risk and stable.

@@

In fisheries science, the commonly used operational models for determining
status and trend of exploited fish populations are stock assessments, i.e.,
population models coupled to an observation model, that incorporate all
appropriate data (e.g. catches, size and age distributions, surveys, and
tagging information) to quantify values such as the biomass of a stock that
can produce maximum sustainable yield ($B_\mathrm{MSY}$) [@hilborn1992].
However, the broad range of data required to conduct these stock assessments
are not available for the majority of fish populations, including those of
conservation concern and of economic interest to fisheries [@fao2014].
Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$
based on the limited data available for the majority of fish stocks: (1) a time
series of the total biomass of catch and (2) a basic understanding of
population productivity [e.g. @vasconcellos2005; @martell2013]. Recently,
@rosenberg2014 investigated the performance of four data-limited models through
a large-scale simulation experiment. Three of these models were based on
Schaefer (logistic) biomass dynamics and one was an empirical model fitted to
more data-rich stock-assessment output. The four models frequently disagreed
about population status (e.g. Fig. \ref{motivate}), no one model had strong
performance across all fish stocks, and some models performed better than
others depending on circumstances.

@@

@@

We first developed and tested ensemble methods on a fully factorial simulated
dataset of fisheries [@rosenberg2014] with known status. These simulated data
included the following scenarios: three fish life histories: small pelagic,
demersal, and large pelagic; three levels of initial biomass depletion
compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying
capacity; and four exploitation settings: (1) a constant exploitation rate,
(2) an exploitation rate coupled with biomass to mimic an open-access
single-species fishery, (3) a scenario where exploitation rate increased
continuously, and (4) a "roller-coaster" scenario where the exploitation
rate increased and then decreased. Process noise (recruitment variability;
i.e. unexplained variability in population dynamics) was introduced to the
models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$,
and was either uncorrelated through time or had first-order autoregressive
correlation of $0.6$. The simulation also included a scenario with $N(0,
0.2^2)$ measurement error around log(catch) and one scenario without
measurement error. @rosenberg2014 ran ten iterations for each combination
of factors adding stochastic draws of recruitment and catch-recording
variability each time to generate a total of 5760 stocks. The simulation
models were built in the `FLR` packages [@kell2007,
<http://flr-project.org>] for the statistical software R. Code to
generate the simulations is available at
<https://github.com/iagomosqueira/stockStatusFAO>.

@@

The individual models we seek to combine with superensembles provide time
series of stock status ($B/B_\mathrm{MSY}$). Therefore, we can use
superensembles to estimate any property of these time series. Here, we focus
on two properties: the mean and slope of $B/B_\mathrm{MSY}$ in the last five
years. Together, these quantities address the recent state and trend of stock
status, which are both of management and conservation interest [e.g. @hutchings2010; @iucn2015]. To avoid undue influence of the time series end points
on the calculated slope, we measured the slope as the Theil-Sen estimator of median slope [@theil1950].

@@

We compared an ensemble average and three superensembles of varying
complexity: a linear model with two-way interactions, a random forest, and a
boosted regression tree. We describe these models as estimating
$\hat{\theta}$, which represents either the ensemble estimated $\log
B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$. The individual model
estimates of $\log B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$ are
represented as $\hat{b}$ for models $i$ $1$ through $4$ (CMSY, SSCOM, COM-SIR, mPRM).
The ensemble average for each fishery $i$ was calculated as:

\begin{equation}
\hat{\theta_i} = \left( \hat{b}_{i,1} + \hat{b}_{i,2} + \hat{b}_{i,3} + \hat{b}_{i,4} \right) / 4, \quad
\mathrm{for}\ i  =  1,...,n.
\end{equation}

@@

\begin{equation}
\hat{\theta_i} = \beta_0 + \beta_1 \hat{b}_{i,1} + ... +
\beta_{1,2} \hat{b}_{i,1} \hat{b}_{i,2} + ... +
\epsilon_i,
\quad
\epsilon \sim \mathrm{Normal}(0, \sigma^2),
\quad \mathrm{for}\ i  =  1,...,n.
\end{equation}

Our two machine learning superensemble models, a random forest and a
generalized boosted model (GBM), were based on regression trees. Regression
trees sequentially determine what value of a predictor best splits the
response data into two branches based on a loss function [@breiman1984]. In
random forests, a series of regression trees are built on a random subset of
the data and random subset of the covariates of the model [@breiman2001]. In
GBMs, each subsequent model is fit to the residuals from the previous model;
data points that are fit poorly in a given model are given more weight in the
next model [@elith2008]. Random forests and GBMs can provide strong predictive
performance and fit highly non-linear relationships [@elith2008; @hastie2009].
We fit random forest models with the `randomForest` package [@liaw2002] for R
with the default argument values. We fit boosted regression tree models with
the `gbm` package [@ridgeway2015] for R. We fit GBMs with 2000 trees, an
interaction depth of $6$, a learning rate (shrinkage parameter) of $0.01$, and
all other arguments at their default values.

@@

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g. @walther2005]. Here, we
measure proportional error, defined as $(\hat{\theta} - \theta)/\abs{\theta}$,
where $\hat{\theta}$ and $\theta$ represent estimated and "true" (or
stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median
proportional error to measure bias, median absolute proportional error to
measure accuracy, and Spearman's rank-order correlation between predicted and
"true" values to measure the ability to correctly rank populations. When
testing with the RAM Legacy Stock Assessment database, we treated the
estimates from these data-rich stock assessments as known without error. Thus,
any error in the stock-assessment estimates of the mean or slope of
$B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for
each of the four data-limited models and the ensembles. Code to reproduce our
analysis is available at <https://github.com/datalimited/ensembles> (*Private while in
review*).

@@

The superensemble models were able to improve the predictive performance by
harnessing the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high
clusters of predictions (Fig. \ref{partial-sim}). SSCOM contributed most strongly on its own to determining trend (Fig. \ref{partial-sim-slope}). Superensembles also exploited
the covariance between individual model predictions. For instance, both the
linear model and GBM ensemble suggest that if mPRM and SSCOM predict high
status, the true status also tends to be high (Figs \ref{lm-coefs},
\ref{partial-2d-sim}l). The addition of spectral density covariates helped the
superensemble models correctly predict higher status values (Fig.
\ref{hexagon-sim-covariates}g, h). The performance of the ensembles was only
marginally improved by including these covariates (Fig.
\ref{performance-with-covariates} vs. Fig. \ref{performance}).

@@

Ensemble methods provide a useful approach to situations where environmental
resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status. Compared to individual models of
fish population status, ensemble methods were consistently the best or among
the best across three performance dimensions (accuracy, bias, and rank-order
correlation), two response variables (status and trend), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a simple
average to machine learning superensembles). Our results suggest choosing a
superensemble model that allows for non-linear relationships, such as
machine learning methods. These methods provide added insight into individual
model behavior and generally performed the best; however, even a simple average
of predictions across multiple models may provide a more useful metric than a single model in many cases.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, and make uncorrelated
errors [@ali1996; @dietterich2000; @tebaldi2007]. We would expect such models
to perform well in different conditions and an ensemble model can
exploit the best predictive performance of each. Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to overfitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we trained our superensembles on
the simulation dataset and tested them on a separate "real" dataset (i.e. the
RAM Legacy Stock Assessment database, Fig. \ref{performance}b). Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically
biased impression of predictive performance if the training dataset
fundamentally differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criterion (AIC) is
a common analytical approach in fisheries and ecology [e.g. @burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890].
A fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. Thus, ensembles
provide a general purpose tool: they do not require information theoretics
and they can combine different types of models (e.g. parametric and
non-parametric models or frequentist and Bayesian predictions). Furthermore,
superensembles extend these benefits by allowing model predictions to be
combined via non-linear functions that are tuned to known data.

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$ (Fig.
\ref{partial-sim}), but contributed strongly to estimates of trend (Fig.
\ref{partial-sim-slope}). Formally, fitting superensemble models to specific
quantities of interest provides an additional calibration step [@rykiel1996].
Individual models are typically calibrated (i.e. parameters are estimated) based
on a single response variable; however, this model might then provide a biased
or inaccurate estimate of other quantities of interest. Ensemble methods provide
a final calibration step to a quantity of interest. This ensemble calibration
could further include a loss function tailored to the goals of the model, say
placing greater weight on accuracy at lower rather than higher status levels.
Conversely, because superensembles are tailored to a specific response and loss
function, superensembles force a modeller to choose an operational purpose for
their model up front [*sensu* @dickey-collas2014].

As @box1987 noted, all models are wrong, but some may still be useful. The
ensemble methods we investigated attempt to piece together the useful parts of
candidate models to build a model with improved performance. Instead of viewing
the superensemble as a black box, we think considerable mechanistic
understanding can be gained by studying its structure. For example, when SSCOM
estimates low status this is likely the case, conversely when COMSIR
estimates low status, the true status is more likely to be high (Fig.
\ref{partial-sim}). These models have two main differences: (1) the form of
effort dynamics and (2) the allowance for both measurement and process error in
SSCOM, whereas the implemented COMSIR admits measurement error only. Were the
methods to differ only in effort dynamics, the results point towards a more
suitable representation of effort dynamics at low biomasses in SSCOM. We think
that such investigation of the structure of a superensemble may lead to
improvement in the mechanisms assumed in the individual models.

Combining predictions from multiple models via superensemble methods is
broadly useful in other subfields of fisheries science and ecology in general.
Predictions about extinction risk are widely used at the national (e.g. the US Endangered
Species Act and the Canadian Species at Risk Act) and international [e.g. the
IUCN Red List, @iucn2015] levels. These risk assessments generally involve
fitting regression models to outcomes for individual species along with
predictors of extinction risk [e.g. @anderson2011a; @pinsky2011], or fitting population-dynamic models to data for individual species [e.g. @dfo2010]. Both types of
models are prone to error caused by model-misspecification and therefore results
are sensitive to decisions about model structure [@brooks2015]. Although there
are options to account for potential model-misspecification in determination of
species risk [e.g. coefficient averaging, @burnham2002; generalized modeling,
@yeakel2011; or semi-parametric methods, @thorson2014], ensemble methods are
a relatively simple way to combine predictions in a transparent manner. Beyond
estimates of status and trend, ensemble methods could be used, for example, to
increase the robustness of spatial predictions when designing networks of
protected areas [@rassweiler2014] or to forecast potential spatial shifts in
species distribution given climate impacts [@harsch2014].

@@

We thank members of Phase I of the working group "Developing new approaches to
global stock status assessment and fishery production potential of the seas"
who contributed to developing the data-limited methods and simulations used in
our analysis. We thank E. Jardim, F. Scott, and J.A. Hutchings for helpful
comments during the development of this project, and R.D. Methot for comments
on an earlier version of the manuscript. We thank the Gordon and Betty Moore
Foundation for funding the working group "Applying data-limited stock status
models and developing management guidance for unassessed fish stocks".
